### 2012-09-03 inst/examples/Reed.Rmd
run for figure3_det, doing deterministic exactly #26

``` {r  SDP_Mat}
pdfn <- function(P, s){
   dunif(P, 1 - s, 1 + s)
#  dlnorm(P, 0, s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

>>>>

``` {r  SDP_Mat}
pdfn <- function(P, s){
   dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

### 2012-09-03 inst/examples/figure3.Rmd
run for figure3_det, doing deterministic exactly #26

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3/", verbose=TRUE or`

@@

@@

``` {r runall}
lvl <- 0.5
low <- scenario(0.1, 0.1, 0.1)
det <- scenario(0.001, 0.00, 0.00)
g   <- scenario(lvl, 0, 0)
m   <- scenario(0, lvl, 0)
i   <- scenario(0, 0, lvl)
````

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3_det/", verbose=TRUE or`

@@

Do the deterministic exactly,

```{r deterministic}
pdfn <- function(P, s){
     dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn)
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r runall}
lvl <- 0.5
low <- scenario(0.1, 0.1, 0.1)
g   <- scenario(lvl, 0, 0)
m   <- scenario(0, lvl, 0)
i   <- scenario(0, 0, lvl)
````
